---
title: "Research"
---
```{r setup, include=FALSE}



###network diagram test
library(tidyverse)
library(igraph)
library(networkD3)
library(ggnetwork)
library(sna)
library(ggiraph)
library(intergraph)
library(stringr)
library(RColorBrewer)

nodes <- read.csv("research_node.csv") %>%
  select(ID, Year, Citation, Data.Science, Local.Government, Budgeting,Peer.Reviewed,
         Books..Encyclopedia.Chapters..Book.Chapters..Book.Reviews..and.Professional.Articles,
         Applied.Research,Type,Status,Weight, Titles)
edges <- read.csv("reseach_edges.csv")
set.seed(12)
net <- graph_from_data_frame(d=edges, vertices=nodes, directed=F)

net2 <- asNetwork(net)

net3 <- ggnetwork(net2, cell.jitter = 7)


gg_point_1 <- 
  ggplot(net3, aes(x = x, y = y, xend=xend, yend=yend, 
                 tooltip = Citation) )  +
  geom_edges() +
  geom_nodes() +
  theme_blank() +
  geom_nodelabel(data = subset(net3, Titles != ""), aes(label = str_wrap(Titles, width = 10), lineheight =.75), fontface = "bold")+
    scale_fill_hue(c=45, l=80)+
  geom_point_interactive(data=subset(net3, Titles==""), aes(color=Type), size = 5) + 
  #scale_colour_discrete("Research Product", labels =  function(x) str_wrap(x, width = 30)) +
  scale_colour_brewer("Research Product", labels =  function(x) str_wrap(x, width = 30),palette = "Set2")#this make the node interactive

gg_point_1

```
```{r vis, echo=FALSE}

girafe(ggobj = gg_point_1) 

```
## CV

[CV Decemeber 1, 2022](https://drive.google.com/file/d/1igwutEHIJMXzI1v0ZqSMPnBzOakbuuHI/view?usp=sharing)

## Municipal Fiscal Health 
  
(Accepted) Rethinking Development and Redistribution Policy: Testing the Local Expenditure Assumption using the Community Development Block Grant Program.  By Michael Overton and Eric Stokan  
  
[50 Years as the 4th Pillar of Public Administration: A Polycentric Extension of the Social Equity Framework.](https://onlinelibrary.wiley.com/doi/10.1111/padm.12888)  By Eric Stokan, Megan Hatch, and Michael Overton  

[Budget Volatility and Economic Base Composition in Local Governments.](https://www.civicresearchinstitute.com/online/article_abstract.php?pid=4&aid=10392&iid=1695)  By Michael Overton and Robert Bland  
  
[Emergent Patterns in Local economic Development in Light of COVID-19.](https://drive.google.com/file/d/1kyCRqvO0gluBtef5Wmh9ephbMx1Ev_BL/view?usp=sharing)  By Brad Johnson, Darrin Wilson, Eric Stokan, and Michael Overton  
  
[Institutional Collective Action During Covid-19: Lessons in Local Economic Development.](https://onlinelibrary.wiley.com/doi/full/10.1111/puar.13234?casa_token=WR05uOppO2EAAAAA%3AZ56QoLLGIpBZ0i6SH-4FCVv7c9wj5luyM8BXMtgnladq-KRE5IdzGqQxA4cj3y5KtC6BHUbcFo1MAWw)  By Darrin Wilson, Brad Johnson, Eric Stokan, and Michael Overton  
  
[Early Payments, Late Payments, and Revenue Volatility in Texas Cities.](https://drive.google.com/file/d/1N4Sd5n7IDRe8FryclcsgJJIKf5JnK_UG/view?usp=sharing)  By Michael Overton, Julius Nukpezah, and Orkhan Ismayilov  
  
[Assessing the Contributions of Collaborators in Public-Private Partnerships: Evidence from Tax Increment Financing.](https://drive.google.com/file/d/1P53CqcBs8TV0XSefcDsa96uiXvbP7LHW/view?usp=sharing)  By Robert Bland and Michael Overton  
  
[The Great Recession’s Impact on Credible Commitment: An Analysis of Private Investment in Tax Increment Financing Districts.](https://drive.google.com/file/d/1tPhuTm5seWmipsMCMWkJEh3im6z1qrCy/view?usp=sharing)  By Michael Overton and Robert Bland  
  
## Data and Data Science
  
[Public Data Primacy: The Changing Landscape of Public Service Delivery as Big Data gets Bigger.](https://link.springer.com/content/pdf/10.1007/s43508-022-00052-z.pdf?pdf=core)  by Michael Overton, Sarah Larson, Lisa Carlson and Stephen Kleinschmit  
  
[Transforming Research Methods Education Through Data Science Literacy.](https://drive.google.com/file/d/1l9Ghi2iS7Bii9-g7ZQvQmkgrFw5PbWT6/view?usp=sharing)  By Michael Overton and Stephen Kleinschmit  

[Data Science Literacy: Towards a Philosophy of Accessible and Adaptable Data Science Skill Development in Public Administration Programs.](https://drive.google.com/file/d/1Ja4YTjbk8Sm1o5564OwvoQ0GNfMXBP7e/view?usp=sharing)  By Michael Overton and Stephen Kleinschmit  

## Competition

[Investigating Sales Tax Revenue Competition among Principal Cities and Their Neighboring Cities in Texas.](https://drive.google.com/file/d/1BHT7SSXy2q0uLPJ7OdgtFJI47gtd6AfG/view?usp=sharing)  By Michael Overton and Julius Nukpezah

[Market Differentiation and the Adoption of Economic Development Strategies: Explaining Policy Adoption in Metropolitan Areas.](https://drive.google.com/file/d/1oMvQ63EK8O6ySWbxvSh_MSBUVWDNlsT4/view?usp=sharing)  By Michael Overton  
  
[Sorting Through the Determinants of Local Government Competition.](https://drive.google.com/file/d/1TjSVvRWeOPAODPKPnyOfquQI4gTroAO5/view?usp=sharing)  By Michael Overton  
  



