---
title: "Research"
---
```{r setup, include=FALSE}



###network diagram test
library(tidyverse)
library(igraph)
library(networkD3)
library(ggnetwork)
library(sna)
library(ggiraph)
library(intergraph)
library(stringr)

nodes <- read.csv("research_node.csv") %>%
  select(ID, Year, Citation, Data.Science, Local.Government, Budgeting,Peer.Reviewed,
         Books..Encyclopedia.Chapters..Book.Chapters..Book.Reviews..and.Professional.Articles,
         Applied.Research,Type,Status,Weight, Titles)
edges <- read.csv("reseach_edges.csv")

net <- graph_from_data_frame(d=edges, vertices=nodes, directed=F)

net2 <- asNetwork(net)

net3 <- ggnetwork(net2, cell.jitter = 3)


gg_point_1 <- 
  ggplot(net3, aes(x = x, y = y, xend=xend, yend=yend, 
                 tooltip = Citation) )  +
  geom_edges() +
  geom_nodes() +
  theme_blank() +
  geom_nodelabel(data = subset(net3, Titles != ""), aes(label = str_wrap(Titles, width = 10), lineheight =.75), fontface = "bold")+
    scale_fill_hue(c=45, l=80)+
  geom_point_interactive(data=subset(net3, Titles==""), aes(color=Type), size = 5) + 
  scale_colour_discrete("Research Product", labels =  function(x) str_wrap(x, width = 30)) #this make the node interactive

gg_point_1

```
```{r vis, echo=FALSE}

girafe(ggobj = gg_point_1) 

```
Check my CV for a list of my research projects!

[CV August 15th, 2021](https://drive.google.com/file/d/1yIxK0g89FBT0oqC8ZvaDw_9B9XE3ddry/view?usp=sharing)

### Peer Reviewed Articles

Overton, Michael and Stephen Kleinschmit.(Forthcoming) "Data Science Literacy: Towards a Philosophy of Accessible and Adaptable Data Science Skill Development in Public Administration Programs." Teaching Public Administration, (Forthcoming).

Overton, Michael, and Robert Bland. (Forthcoming) “Exploring the Linkage between Economic Base, Revenue Growth, and Revenue Stability in Large Municipal Governments.” Municipal Finance Journal, (Forthcoming).

Wilson, Darrin, Brad Johnson, Eric Stokan, and Michael Overton. (2020) “Institutional Collective Action During Covid-19: Lessons in Local Economic Development.” Public Administration Review, 80 (5).

Overton, Michael and Julius Nukpezah. (2020) “Investigating Sales Tax Revenue Competition among Principal Cities and Their Neighboring Cities in Texas.” International Journal of Public Administration, 43 (11).

Overton, Michael. (2018) “Market Differentiation and the Adoption of Economic Development Strategies: Explaining Policy Adoption in Metropolitan Areas.” The Review of Regional Studies, 48 (3).

Overton, Michael, Julius Nukpezah, and Orkhan Ismayilov. (2017) “Early Payments, Late Payments, and Revenue Volatility in Texas Cities.” Public Money & Management, 38 (7).

Overton, Michael. (2017) “Sorting Through the Determinants of Local Government Competition.” The American Review of Public Administration, 47 (8).

Bland, Robert and Michael Overton. (2016) “Assessing the Contributions of Collaborators in Public-Private Partnerships: Evidence from Tax Increment Financing.” The American Review of Public Administration, 46 (4).

Overton, Michael and Robert Bland. (2014) “The Great Recession’s Impact on Credible Commitment: An Analysis of Private Investment in Tax Increment Financing Districts.” State and Local Government Review, 46 (4).

### Encyclopedia Chapters, Book Chapters, and Book Reviews

Overton, Michael. (2021) “Book Review of the Public Affairs Faculty Manual.” Journal of Public and Nonprofit Affairs, 7 (2).

Nukpezah, Julius, and Michael Overton. (2020) “Vertical and Horizontal Tax Competition in the USA.” In: Farazmand A. (ed.) Global Encyclopedia of Public Administration, Public Policy, and Governance. Springer, Cham. https://doi.org/10.1007/978-3-319-31816-5_3936-1

### Books

Bland, Bland, Robert, and Michael Overton. (2019) A Budgeting Guide for Local Government. 4th ed. International City/County Management Association: Washington, DC

### Professional Articles

Bland, Robert, and Michael Overton. (2020) Building Better Communities through Better Budgeting. PM Magazine, February.

### Applied Research and Grant Reports

Overton, Michael, Eric Stokan, Brian Ellison, and Bruce Godfrey. (2020) “Community Development Block Grants and Local Economic Development.” Prepared for the U.S. Department of Housing and Urban Development.

Overton, Michael, and Juliet Carlisle. (2018) “SMART Transit Ridership and Community Survey: Results and Final Report.” Prepared for SMART Transit.

Overton, Michael, and Robert Bland. (2017) “Exploring the Linkage between Economic Base, Revenue Growth, and Revenue Stability in Large Municipal Governments.” Prepared for the Lincoln Institute of Land Policy’s Municipal Fiscal Health Initiative.

Overton, Michael, and Robert Bland. (2017) “The Impact of Industrial Diversification and Clustering on the Volatility of City Budgets.” Prepared for the Lincoln Institute of Land Policy’s Municipal Fiscal Health Initiative.

Overton, Michael. (2016) “The Economic Impacts of Transportation Corridors.” Prepared for the North Central Texas Council of Governments-Transportation Department.

Bland, Robert, Robert Bland, and Patrick Shinkle. (2016) “State Appropriation Forecasts for Academic Year 2016-2017.” Prepared for the Division of Finance and Administration in the University of North Texas.

Shinkle, Patrick, Michael Overton, and Robert Bland. (2015) “Tuition Dashboard.” Prepared for the Division of Finance and Administration in the University of North Texas.

Overton, Michael, Patrick Shinkle, and Robert Bland. (2015) “Tuition Elasticity Dashboard.” Prepared for the Division of Finance and Administration in the University of North Texas.



